Delta Factor - A New Authorization Factor

### 2022-08-09 paper1.tex
updated again

%---------------------------------------------------------------------------------------------------------------------
% Still following exactly professor's Canvas example
\section{Design Principles}
% ppt frames 11 , 12 , 13 , 14 . 15
% Paragraph 1: a general overview of the techniques that we used
\noindent	% frame 			15
Design Goals:\\
• Methodology to work on any OS, Windows 10, OSX, Linux distributions, and Mobile\\
• Ability to work on websites today, without loss of security or privacy\\
• Anyone anywhere, should be able to use this to verify a website\\
• Users should have the tool and ability to detect MITMs\\
• Transparent MITM should be harder.\\

@@

%--------------------------------------------------------------------------------------------------------------------
\section{Experiment}				% Still following exactly professor's Canvas example
\subsection{Setup}
Due to the nature of this proposal, a proper experiment requires a large body of people to understand how much more effective this is at detection of MITM vs a control (such as regular 2FA) Time constraints didn't allow us to gather the people needed for such a trial. However, from running these code itself, we can take a look at some areas where this method may fall apart and propose some solutions.

The setup for this experiment is a simple proof of concept webserver. The webserver uses URIs to indicate protected data. The client will use a web browser to access this webserver and it's protected resource. The resource will simply be the client's username - and accessing this page will trigger the server generate an one-time password, and embed this information into presented page. The client's web browser also includes the instrumentation to generate a one-time password via a browser extension/plug in.

@@

%------------------------------------------------------------------------------%---------------------------------------
%------------------------------------------------------------------------------%---------------------------------------
\section{CITATIONS \normalfont{(Chicago style):}} 	% Same as "References" as per prof

>>>>

%---------------------------------------------------------------------------------------------------------------------
% Still following exactly professor's Canvas example
\section{Design Principles}
% ppt frames 11 , 12 , 13 , 14 . 15
% Paragraph 1: a general overview of the techniques that we used
\noindent	% frame 			15
Design Goals:\\
• Methodology to work on any OS, Windows 10, OSX, Linux distributions, and Mobile\\
• Ability to work on websites today, without loss of security or privacy\\
• Anyone anywhere, should be able to use this to verify a website\\
• Users should have the ability to detect MITMs\\

@@

%--------------------------------------------------------------------------------------------------------------------
\section{Experiment}				% Still following exactly professor's Canvas example
\subsection{Setup}
Due to the nature of this work, a proper experiment could not be performned. A statistically significant sample of people is needed to determine detection rate of MITMs against a control. Time constraints didn't allow us to gather the people needed for such a trial. However, from running the code, we took a look at areas where the proposed method may fall apart and investigated some solutions.

The setup for this experiment is a proof of concept webserver. The webserver will have a valid server certificate, a reverse proxy, and a simple application serving content. The webserver uses URIs to indicate protected data. For example, URI other than the index page, is considered a protected resource. The client will use a web browser to access the webserver. The client will attempt to access a protected resource. The webserver checks if the resource has been assiocated with a secret that's been shared. If it's already been shared to a client, then a COTP is presented. If there's no secret assiocated with the resource, then an input field is provided to allow the client to provide a secret. The generated one-time password is inserted into the body of the returned application layer HTML.

The client's web browser also includes the instrumentation to generate a one-time password via a browser extension/plug in. This one-time password will use a secret either generated randomly or provided by the client directly. The secret will act as the private key used for signing the message in the HMAC-SHA1 algorithm. The message will be a concatenation of features / factors assiocated with the one-time password algorithm.

@@

\subsubsection{Implications}
Using these methods as both an authenication check for both the server and client is important. Due to connection details being easily accessible by attacks, either as the MITM or passively through traffic analysis.

A strong method assiocate small deltas to the same number while large deltas to another while having access to a single number - is a hard problem. Here we use a prime as windowing function.This isn't ideal - as there's also cases where both latences have a small delta but map to different windows. Consider 7ms window with server round-trip-time of 6ms and client round-trip-time of 8ms. Small delta of 2ms, but map to completely different windows. Using a smaller prime number with the server providing multiple COTPs using a the previous, current, and next window is also possible. This method is similiar to how TOPT handles time frames.

%------------------------------------------------------------------------------%---------------------------------------
\section{CITATIONS \normalfont{(Chicago style):}} 	% Same as "References" as per prof
